Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-15 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
sect. 4

In this section, we present an algorithm for \textsc{Online Multiclass
Classification with Bandit Feedback} and prove an upper bound on the number of
mistakes under the assumption that the examples are strongly linearly separable
with a margin. The algorithm is stated as
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
the mistake upper bound is stated as
\autoref{theorem:strongly-separable-examples-mistake-upper-bound}.

The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
Perceptron} algorithm, where each copy corresponds to a class. In each round,
copy $i$ makes a binary prediction, indicating whether the example belongs to
class $i$ or not. If at least one copy makes a positive prediction, the
algorithm chooses its prediction as one of the classes corresponding to a
positive prediction. If all copies make negative predictions, the algorithms
makes a prediction uniformly at random.

@@

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-examples-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
  \item the examples are strongly linearly separable with margin $\gamma$ (Definition~\ref{definition:strong-linear-separability}),
  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
\end{enumerate}
then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

\begin{proof}
Let $M = \sum_{t=1}^T z_t$ be the number of
mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
Let $A
= \sum_{t ~:~ S_t \neq \emptyset} z_t$ be the number of mistakes in the rounds
when $S_t \neq \emptyset$ and let $B = \sum_{t ~:~ S_t = \emptyset} z_t$ be the
number of mistakes in the rounds when $S_t = \emptyset$.
It can be easily seen that $M = A + B$.

Let $C$ be the number of times line~\ref{line:pos-update} gets executed. Let $U$
be the number of times line~\ref{line:pos-update} or line~\ref{line:neg-update}
get executed. In other words, $U$ is the number of times the $K$-tuple of
vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
easily seen that $U = A + C$.

The key observation is that $\Exp[B] = (K-1) \Exp[C]$. The equality holds
because if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
guesses the correct label and with probability $(K-1)/K$ algorithm's guess is
incorrect. Putting all the information together, we get that
\begin{align}
\Exp[M]
& = \Exp[A] + \Exp[B] \nonumber \\
& = \Exp[A] + (K-1) \Exp[C] \nonumber \\
& \le (K-1) \Exp[A + C] \nonumber\\
& = (K-1) \Exp[U]  \; .
\label{eqn:mistake-update}
\end{align}

>>>>

In this section, we present an algorithm for \textsc{Online Multiclass
Classification with Bandit Feedback}, namely Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}.
Under the assumption that the examples are strongly linearly separable
with a margin (Definition~\ref{definition:strong-linear-separability}),
we prove \autoref{theorem:strongly-separable-examples-mistake-upper-bound},
which gives an upper bound on its number of mistakes.

%The algorithm is stated as
% and
%the mistake upper bound is stated as.

The idea behind Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
 is to use $K$ copies of the \textsc{Binary
Perceptron} algorithm,
\chicheng{Shall we define the binary Perceptron algorithm?}
where each copy corresponds to a class. At each timestep $t$, upon seeing
example $x_t$,
copy $i$ makes a binary prediction on whether $x_t$ belongs to
class $i$ or not. If at least one copy makes a positive prediction, the
algorithm chooses its prediction as one of the classes corresponding to a
positive prediction. If all copies make negative predictions, the algorithms
makes a prediction uniformly at random.

@@

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-examples-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that:
\begin{enumerate}
  \item $L$ is strongly linearly separable with margin $\gamma$,
  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
\end{enumerate}
then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

%$A
%= \sum_{t ~:~ S_t \neq \emptyset} z_t$
%B = \sum_{t ~:~ S_t = \emptyset} z_t
%\sum_{t ~:~ S_t = \emptyset}
\begin{proof}
Let $M = \sum_{t=1}^T z_t$ be the number of
mistakes Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} makes.
Let $A = \sum_{t=1}^T \one[S_t \neq \emptyset] z_t$ be the number of mistakes in the rounds
when $S_t \neq \emptyset$, i.e. the number of rounds line~\ref{line:neg-update} is
executed.
In addition, let $B = \sum_{t=1}^T \one[S_t = \emptyset] z_t$ be the
number of mistakes in the rounds when $S_t = \emptyset$.
It can be easily seen that $M = A + B$.

Let $C = \sum_{t=1}^T \one[S_t = \emptyset](1 - z_t)$ be the number of rounds
line~\ref{line:pos-update} gets executed. Let
$U = \sum_{t=1}^T (\one[S_t \neq \emptyset] z_t + \one[S_t = \emptyset](1 - z_t))$
be the number of rounds line~\ref{line:pos-update} or~\ref{line:neg-update}
gets executed. In other words, $U$ is the number of times the $K$-tuple of
vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets updated. It can be
easily seen that $U = A + C$.

The key observation is that $\Exp[B] = (K-1) \Exp[C]$.
To see this, note that if $S_t = \emptyset$, there is $1/K$ probability that the algorithm
guesses the correct label ($z_t = 0$) and with probability $(K-1)/K$ algorithm's guess is
incorrect ($z_t = 1$). Therefore,
\[ \Exp[ z_t |S_t = \emptyset] = \frac{K-1}{K}, \]
\[ \Exp[B] = \frac{K-1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }, \]
\[ \Exp[C] = \frac{1}{K} \Exp \sbr{ \sum_{t=1}^T \one[S_t = \emptyset] }. \]

Putting all the information together, we get that
\begin{align}
\Exp[M]
& = \Exp[A] + \Exp[B] \nonumber \\
& = \Exp[A] + (K-1) \Exp[C] \nonumber \\
& \le (K-1) \Exp[A + C] \nonumber\\
& = (K-1) \Exp[U]  \; .
\label{eqn:mistake-update}
\end{align}

### 2019-01-15 ICML-submission/notions-of-linear-separability.tex
sect. 4

\begin{definition}[Weak linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{weakly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $(x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T)$ be labeled examples in $V \times \{1,2,\dots,K\}$.

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{definition}

The notion of weak linear separability with a margin is standard. It is used in
the full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. It is a folklore result that if a set
of labeled examples is separable with a margin $\gamma$ and the norm of the
examples is bounded by $R$, then \textsc{Multiclass Perceptron} algorithm makes
at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore
result is that \textsc{Multiclass Perceptron} is essentially optimal in the
sense that any deterministic algorithm must make $\left\lfloor (R/\gamma)^2
\right \rfloor$ mistakes in the worst case. For completeness, we state the
\textsc{Multiclass Perceptron} algorithm and give proofs of both of these
results in Appendix~\ref{section:multiclass-perceptron-proofs}.

The notion of strong linear separability has appeared in the literature; see
e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
Intuitively, strong linear
separability means that, for each class $i$, the set of examples belonging to
class $i$ and the set of example belonging to the remaining $K-1$ classes are
separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.

It is easy to see that if a set of labeled examples are strongly linearly
separable with margin $\gamma$, then they are weakly linearly separable with
the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$
satisfy \eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

In the special case of $K=2$, if a set of labeled examples are weakly linearly
separable with a margin $\gamma$, then they are strongly linearly separable with
the same margin. Indeed, if $w_1, w_2$ satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
$w_2' = \frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}. The first condition follows from
$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
The last two condition follows from the fact that $w_1' - w_2' = w_1 - w_2$.

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable
with a positive margin $\gamma$ but it is not strongly linearly separable with
any positive margin $\gamma$. An example of such set of labeled examples is
shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.

>>>>

\begin{definition}[Weak linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T))$ be a set of labeled examples in $V \times \{1,2,\dots,K\}$.
\chicheng{This $L$ notion may be a bit confusing - feel free to edit}

$L$ is said to be \emph{weakly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; .
\end{gathered}
\end{align}
\end{definition}

\begin{definition}[Strong linear separability]
\label{definition:strong-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. Let $L = ((x_1, y_1), (x_2,
y_2), \dots, (x_T, y_T))$ be labeled examples in $V \times \{1,2,\dots,K\}$.

$L$ is said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \frac \gamma 2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \frac \gamma 2 \; .
\end{gathered}
\end{align}
\end{definition}

The notion of weak linear separability with a margin is standard. It is used in
the full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. It is a folklore result that if a set
of labeled examples is separable with a margin $\gamma$ and the norm of the
examples is bounded by $R$, then \textsc{Multiclass Perceptron} algorithm makes
at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$ mistakes. Another folklore
result is that \textsc{Multiclass Perceptron} is essentially optimal in the
sense that any deterministic algorithm must make $\left\lfloor (R/\gamma)^2
\right \rfloor$ mistakes in the worst case.
\chicheng{And any randomized algorithm must make $\left\lfloor (R/\gamma)^2
\right \rfloor / 2$ mistakes?}
For completeness, we state the
\textsc{Multiclass Perceptron} algorithm and give proofs of both of these
results in Appendix~\ref{section:multiclass-perceptron-proofs}.

\chicheng{Shall we mention the multiclass margin notion that appeared in e.g.}

The notion of strong linear separability has appeared in the literature; see
e.g.~\citet{Chen-Chen-Zhang-Chen-Zhang-2009}.
Intuitively, strong linear
separability means that, for each class $i$, the set of examples belonging to
class $i$ and the set of examples belonging to the remaining $K-1$ classes are
separated by a linear classifier $w_i$ by a margin $\frac \gamma 2$.

It is easy to see that if a set of labeled examples are strongly linearly
separable with margin $\gamma$, then it is also weakly linearly separable with
the same margin. Indeed, if $w_1, w_2, \dots, w_K \in V$
satisfy \eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3} then they satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

In the special case of $K=2$, if a set of labeled examples are weakly linearly
separable with a margin $\gamma$, then it is also strongly linearly separable with
the same margin. Indeed, if $w_1, w_2$ satisfy
\eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2} then $w_1' = \frac{w_1 - w_2}{2}$,
$w_2' = \frac{w_2 - w_1}{2}$ satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2},
\eqref{equation:strong-linear-separability-3}.
Equation~\eqref{equation:strong-linear-separability-1} follows from
$\norm{w_i'}^2 \le (\frac{1}{2} \norm{w_1} + \frac{1}{2} \norm{w_2})^2 \le
\frac{1}{2}\norm{w_1}^2 + \frac{1}{2}\norm{w_2}^2 \le \frac{1}{2}$ for $i=1,2$.
Equations~\eqref{equation:strong-linear-separability-2} and~\eqref{equation:strong-linear-separability-3} follow from the fact that $w_1' - w_2' = w_1 - w_2$.

However, for any $K \ge 3$ and any inner product space of dimension at least
$2$, there exists a set of labeled examples that is weakly linearly separable
with a positive margin $\gamma$ but is not strongly linearly separable with
any positive margin $\gamma$. An example of such set of labeled examples is
shown in~\autoref{figure:weakly-linearly-separable-examples-with-margin}.

### 2019-01-15 ICML-submission/related-work.tex
sect. 4

The problem of bandit multiclass linear classification was initially formulated
in the pioneering work of~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed
two computationally inefficient algorithms that work in the standard
linearly separable setting, one with a mistake bound of $O(K^2 d
\ln(\frac{d}{\gamma^2}))$, the other with a mistake bound of
$\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$. In addition, the authors propose
the \textsc{Banditron} algorithm, a computationally efficient algorithm that has
a $O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak linearly separable
setting. The polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in the margin parameter can be obtained.

%Whether one can design an efficient algorithm with a finite mistake bound that
%has no dimensionality dependence is mentioned as an open problem in
%~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a
%positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$

Many works consider bandit multiclass classification in the general
non-separable setting. \citet{Abernethy-Rakhlin-2009} poses the open problem of
whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
such an algorithm can be obtained, provided that the distribution of the label
$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
logistic loss, where the exact order of the regret depends on the diameter of
the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
$\widetilde{O}(\sqrt{T})$ against the
$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
bound does not depend sensitively on the diameter of the benchmark class.
\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
dependence on the diameter of the benchmark class.

\citet{Chen-Lin-Lu-2014} and \citet{Zhang-Jung-Tewari-2018} study online bandit
multiclass boosting under bandit feedback, where one can view online boosting as
online linear classification by treating each base hypothesis as a separate
feature. \citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
the set of examples is strongly separable by a convex combination of base
hypotheses with a margin. Under this condition, it gives an algorithm with a
$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
weak learning condition, which implies that all examples is separable by a
convex combination of base hypotheses with a margin; see~\citet[Theorem
3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.

The online bandit multiclass learning is a special case of the contextual
bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
classification error. A series of works in the contextual bandits learning
literature focuses on oracle-efficiency, that is, they assume access to an
oracle that given a set of cost-sensitve learning examples.

There has been much literature on the contextual bandit learning
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observed the incurred cost $c_t$. The goal of the learner is to
minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
\sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
special case of the contextual bandits problem, where the cost $c_t(i)$ is the
classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the set of
linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$. A
series of works in the contextual bandits learning literature focus on
oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
a policy optimization oracle that receives a set of cost-sensitive learning
examples and policy class $\Pi$, return the policy in $\Pi$ that minimizes its
empirical cost on the examples, and the algorithm only call the oracle a
polynomial number of times. However, these algorithms are not truly
computationally efficient in our setting, as it is NP-hard in general to find a
linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

%as algorithms generate cost-sensitive examples that may not be linearly
%separable Algorithms that satisfy oracle efficiency has been proposed in the
%literature, for example.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on benchmarks of the form
$\min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
)$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s \gamma, 0)$ or $\min(1,
\max(1 - \frac s \gamma, 0))$. On one hand, it gives information-theoretic
mistake upper bounds under various settings of $\calF$, including parametric and
nonparametric classes. On the other hand, it gives an efficient algorithm that
has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x:
W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
the online bandit multiclass learning problem yields an algorithm with a
$O(\sqrt{T})$ mistake bound in the strong linearly separable setting.

>>>>

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak reinforcement
model''. They showed that if all examples shown agrees with some
classifier in a prespecified hypothesis class $\calH$, then the optimal mistake
bound in the bandit setting can be upper bounded by the optimal mistake bound in
the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed its
 near-optimality.
\citet{Daniely-Helbertal-2013} extended the results to the setting where the
performance of the algorithm is measured by its regret, i.e. the difference
between the number of mistakes made by the algorithm and the number of mistakes
made by the best classifier in $\calH$ in hindsight. However, all algorithms
developed in this context are computationally inefficient.

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of $O(K^2 d \ln(\frac{d}{\gamma}))$, the other with a
mistake bound of $\widetilde{O}(\frac{K^2}{\gamma^2} \ln T)$.
The latter result was later improved by \citet{Daniely-Helbertal-2013},
which gives a computationally inefficient algorithm with a mistake
upper bound of $\widetilde{O}(\frac{K}{\gamma^2})$.
In addition, the
authors propose the \textsc{Banditron} algorithm, a computationally efficient
algorithm that has a $O(T^{2/3})$ regret against the multiclass hinge loss in
the general setting, and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weak
linearly separable setting. The polynomial dependence of \textsc{Banditron}'s
mistake bound on the time horizon is undesirable for problems with a long time
horizon. One key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}
is whether one can design computationally efficient algorithms that achieve
mistake bounds that match or improve over those of inefficient algorithms. In
this paper, we take a step towards answering this question, showing that
efficient algorithms with mistake bounds quasipolynomial in $\frac 1 \gamma$
or quasipolynomial in $K$ can be obtained.

%In addition, it also
% shows that under different relationships between $k$, $d$ and $\gamma$,
% the adversary can force the learner to incur $\Omega(K^2 d)$
% or $\Omega(\frac{K}{\gamma^2})$ mistakes.

%Whether one can design an efficient algorithm with a finite mistake bound that
%has no dimensionality dependence is mentioned as an open problem in
%~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, where in this paper we provide a
%positive answer. $O(k^2 d \ln(\frac{d}{\gamma^2}))$
\chicheng{I significantly shortened the discussions of all those $\sqrt{T}$
regret algorithms here, as I think they are not very relevant.}

Many works consider bandit multiclass classification in the general setting,
where the data is not necessarily separable by some linear
classifier~\cite{Abernethy-Rakhlin-2009,
Wang-Jin-Valizadegan-2010,
Crammer-Gentile-2013,
Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
Foster-Kale-Luo-Mohri-Sridharan-2018}.
In addition, \citet{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit
multiclass boosting under bandit feedback, where one can view boosting as
linear classification by treating each base hypothesis as a separate
feature.
However, most of these works achieve a regret bound of order $\widetilde{O}(\sqrt{T})$
to $O(T^{3/4})$. In the weakly separable setting, these algorithms
only guarantees a mistake upper bound of $\widetilde{O}(\sqrt{T})$, which is
undesirable for problems with a long time horizon.
One exception is the \textsc{Newtron} algorithm, where with appropriate
settings of parameter $\alpha$, it is able to achieve a $O(\ln T)$ regret.
However, as argued
in ~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of $\alpha$
makes the regret bound $O(\sqrt{T})$, the logistic loss of the best linear
predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} is still only
able to guarantee a mistake upper bound of $O(\sqrt{T})$ in the weakly separable setting.

%\citet{Abernethy-Rakhlin-2009} poses the open problem of
%whether one can design an efficient algorithm to get a $O(\sqrt{T})$ regret
%against some reasonable loss functions. \citet{Crammer-Gentile-2013} show that
%such an algorithm can be obtained, provided that the distribution of the label
%$y_t$ conditioned on feature vector $x_t$ satisfies certain parametric noise
%assumption. \citet{Hazan-Kale-2011} developed the \textsc{Newtron} algorithm,
%which has a regret between $O(\ln T)$ and $O(T^{2/3})$ against the multiclass
%logistic loss, where the exact order of the regret depends on the diameter of
%the benchmark class. In particular, if the diameter is $O(\ln T)$, its regret
%bound would become $O(T^{2/3})$. The \textsc{SOBA} algorithm by
%\citet{Beygelzimer-Orabona-Zhang-2017} achieves a regret of
%$\widetilde{O}(\sqrt{T})$ against the
%$\eta$-loss~\citet{Orabona-Cesa-Bianchi-Gentile-2012}. In addition, its regret
%bound does not depend sensitively on the diameter of the benchmark class.
%\citet{Foster-Kale-Luo-Mohri-Sridharan-2018} developed an algorithm that has a
%regret of $\widetilde{O}(\sqrt{T})$ against the multiclass logistic loss, where
%it doubly-exponentially improves over \citet{Hazan-Kale-2011}'s regret on its
%dependence on the diameter of the benchmark class.

%\citet{Chen-Lin-Lu-2014}'s online weak learning condition implies that
%the set of examples is strongly separable by a convex combination of base
%hypotheses with a margin. Under this condition, it gives an algorithm with a
%$O(T^{3/4})$ mistake bound. \citet{Zhang-Jung-Tewari-2018} considers an online
%weak learning condition, which implies that all examples is separable by a
%convex combination of base hypotheses with a margin; see~\citet[Theorem
%3]{Mukherjee-Schapire-2013}. Under this condition, it gives a boosting algorithm
%with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge parameter. In
%addition, it gives an adaptive algorithm with a $O(T^{3/4})$ mistake bound.

%Online bandit multiclass learning is a special case of the contextual
%bandits problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
%classification error. A series of works in the contextual bandits
%literature focuses on oracle-efficiency, that is, they assume access to an
%oracle that given a set of cost-sensitve learning examples, generates .

There is a large body of literature on the contextual bandit learning
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$.
The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{\pi \in \Pi}
\sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass learning problem is a
special case of the contextual bandits problem, where the cost $c_t(i)$ is the
classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the set of
linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$. A
series of works in the contextual bandits learning literature focus on
oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
a policy optimization oracle that can return the policy in $\Pi$ that minimizes its
empirical cost on any set of cost-sensitive examples, and the algorithm only calls the oracle a
polynomial number of times. However, these algorithms are not truly
computationally efficient in our setting, as it is NP-hard in general to find a
linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

%that receives a set of cost-sensitive learning
%examples and policy class $\Pi$,
%as algorithms generate cost-sensitive examples that may not be linearly
%separable Algorithms that satisfy oracle efficiency has been proposed in the
%literature, for example.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t)
)$, where $\calF$ contains score functions $f$ such that $\sum_{i=1}^K
f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s \gamma, 0)$ or $\min(1,
\max(1 - \frac s \gamma, 0))$. On one hand, it gives information-theoretic
mistake upper bounds under various settings of $\calF$, including parametric and
nonparametric classes. On the other hand, it gives an efficient algorithm that
has a $O(\sqrt{T})$ regret against the benchmark of $\calF = \cbr{x \mapsto W x:
W \in \R^{k \times d}, \one^T W = 0}$. A direct application of this result to
online bandit multiclass linear classification yields an algorithm with a
$O(\sqrt{T})$ mistake bound in the strongly linearly separable setting.
